---
output:
  pdf_document: default
  html_document: default
---
```{r}
# Load necessary libraries and data
library(survival)
library(tidyverse)
library(mice)
data(lung, package="survival")
larynx <- lung

# Create description table
summary(larynx)
table(larynx$sex)
table(larynx$age)
table(larynx$ph.ecog)
table(larynx$ph.karno)
table(larynx$pat.karno)
table(larynx$meal.cal)
table(larynx$wt.loss)

```
```{r}
library(survival)
library(tidyverse)
library(mice)

# Load data
data(lung, package = "survival")
larynx <- lung

# Create a function to calculate percentage or median based on data type
percent_or_median <- function(x) {
  if (is.numeric(x)) {
    median(x, na.rm = TRUE)
  } else if (is.logical(x)) {
    percent_true <- sum(x, na.rm = TRUE) / length(x) * 100
    paste0(round(percent_true, 2), "%")
  } else {
    NA
  }
}

# Create description table
larynx_desc <- larynx %>%
  summarize_all(percent_or_median) %>%
  t() %>%
  as.data.frame(stringsAsFactors = FALSE) %>%
  setNames("Value") %>%
  mutate(Variable = rownames(.))

# Print description table
print(larynx_desc)

```
```{r}
library(survival)
library(tidyverse)
library(mice)

# Load data
data(lung, package = "survival")
larynx <- lung

# Define a function to calculate median and bias
median_and_bias <- function(x) {
  median_val <- median(x, na.rm = TRUE)
  bias_val <- median_val - mean(x, na.rm = TRUE)
  return(c(median_val, bias_val))
}

# Define a function to calculate percentage
percentage <- function(x) {
  mean_val <- mean(x, na.rm = TRUE)
  return(mean_val * 100)
}

# Create a data frame with variables and their descriptions
desc_table <- data.frame(
  variable = c("Age", "Sex", "Ph.ecog", "Ph.karno", "Pat.karno", "Meal.cal", 
               "Wt.loss", "Survival", "Celltype", "Stage", "Rstatus"),
  description = c("Age in years",
                  "Sex (male = 1, female = 2)",
                  "ECOG performance status (0=good 5=dead)",
                  "Karnofsky performance score (bad=0-good=100)",
                  "Karnofsky performance score (bad=0-good=100)",
                  "Calories consumed at each meal",
                  "Weight loss in last six months",
                  "Survival time in days",
                  "Cell type (small cell/large cell)",
                  "Extent of disease (stage I to IV)",
                  "Recurrent status (yes=1, no=2)"
  ),
  median = apply(larynx[, c("Age", "Ph.ecog", "Ph.karno", "Pat.karno", "Meal.cal", "Wt.loss", "Survival")], 2, median_and_bias),
  bias = apply(larynx[, c("Age", "Ph.ecog", "Ph.karno", "Pat.karno", "Meal.cal", "Wt.loss", "Survival")], 2, median_and_bias),
  percentage = apply(larynx[, c("Sex", "Celltype", "Stage", "Rstatus")], 2, percentage)
)

# Print the description table
print(desc_table)

```

```{r}
# Load required packages
library(survival)
library(tidyverse)
library(corrplot)
# Load data
data(lung)
data(cancer, package="survival")
larynx=lung
larynx=larynx%>%drop_na()

# Convert variables to required format
larynx$age <- as.numeric(scale(larynx$age))
larynx$inst <- as.factor(scale(larynx$inst))
larynx$sex <- as.factor(scale(larynx$sex))
larynx$ph_ecog <- as.factor(scale(larynx$ph.ecog))
larynx$ph_karno <- as.factor(scale(larynx$ph.karno))
larynx$pat_karno <- as.factor(scale(larynx$pat.karno))
larynx$meal_cal <- as.numeric(larynx$meal.cal)
larynx$wt_loss <- as.numeric(larynx$wt.loss)

# Exploratory data analysis
# Histograms
ggplot(larynx, aes(x = time)) + geom_histogram()
ggplot(larynx, aes(x = status)) + geom_histogram()

# Boxplots
ggplot(larynx, aes(x = sex, y = time)) + geom_boxplot()
ggplot(larynx, aes(x = inst, y = time)) + geom_boxplot()

# Scatter plot
ggplot(larynx, aes(x = age, y = time)) + geom_point()

# Correlation plot
cor_plot <- cor(larynx[, c("time", "status", "age", "meal_cal", "wt_loss")])
corrplot(cor_plot)

# Survival analysis
# Kaplan-Meier estimator
km_fit <- survfit(Surv(time, status) ~ 1, data = larynx)
plot(km_fit)

```


```{r}
library(tidyverse)
library(survival)
data(lung)
data(cancer, package="survival")
larynx=lung
larynx=na.omit(larynx)
larynx
library(corrplot)
library(psych)
larynx_cont = larynx %>%
  select_if(is.numeric) %>%
  na.omit()
corr_matrix = cor(larynx_cont)
corrplot(corr_matrix, method = "circle", type = "lower")
fa_results = fa(larynx_cont, nfactors = 3, rotate = "varimax")
print(fa_results, sort = TRUE, digits = 2)

covariates <- c("inst","age", "sex",  "ph.karno", "ph.ecog", "wt.loss","pat.karno","meal.cal","wt.loss")
univ_formulas <- sapply(covariates,
                        function(x) as.formula(paste('Surv(time, status)~', x)))
                        
univ_models <- lapply( univ_formulas, function(x){coxph(x, data = larynx)})
# Extract data 
univ_results <- lapply(univ_models,
                       function(x){ 
                          x <- summary(x)
                          p.value<-signif(x$wald["pvalue"], digits=2)
                          wald.test<-signif(x$wald["test"], digits=2)
                          beta<-signif(x$coef[1], digits=2);#coeficient beta
                          HR <-signif(x$coef[2], digits=2);#exp(beta)
                          HR.confint.lower <- signif(x$conf.int[,"lower .95"], 2)
                          HR.confint.upper <- signif(x$conf.int[,"upper .95"],2)
                          HR <- paste0(HR, " (", 
                                       HR.confint.lower, "-", HR.confint.upper, ")")
                          res<-c(beta, HR, wald.test, p.value)
                          names(res)<-c("beta", "HR (95% CI for HR)", "wald.test", 
                                        "p.value")
                          return(res)
                          #return(exp(cbind(coef(x),confint(x))))
                         })
```
```{r}
res <- t(as.data.frame(univ_results, check.names = FALSE))
as.data.frame(res)
res.cox <- coxph(Surv(time, status) ~inst+  ph.karno +pat.karno+age + sex + ph.ecog+inst +  meal.cal + wt.loss, data = larynx)
summary(res.cox)

```
```{r}
###?????
library(survival)

# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data
cens <- matrix(c(larynx$time, larynx$status), ncol=2)
larynx$status <- ifelse(larynx$status==1, 0, 1)

# Impute missing values in inst 33 using the same method as in full_data dataset
larynx$M <- rbinom(nrow(larynx), prob = exp(1.2-0.1*larynx$pat.karno)/(1+exp(1.2-0.1*larynx$pat.karno)), size = 1)
larynx$N_obs <- ifelse(larynx$M == 1, larynx$inst33, NA)

# Fit Cox PH model
coxph_model <- coxph(Surv(time, status) ~ sex + age + ph.ecog + ph.karno + pat.karno + meal.cal + wt.loss, data=larynx)

# Print summary of the model
summary(coxph_model)

# Calculate hazard ratios and 95% confidence intervals
exp(cbind(coef(coxph_model), confint(coxph_model)))

# Test the proportional hazards assumption
cox.zph(coxph_model)

# Plot the survival curves
library(survminer)
ggsurvplot(survfit(coxph_model), data=larynx)

```

```{r}
#partialinstall
library(survival)

```# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data
cens <- matrix(c(larynx$time, larynx$status), ncol=2)
larynx$status <- ifelse(larynx$status==1, 0, 1)

# Fit Cox PH model
coxph_model <- coxph(Surv(time, status) ~ sex + age + ph.ecog + ph.karno + pat.karno + meal.cal + wt.loss, data=larynx)

# Print summary of the model
summary(coxph_model)

# Calculate hazard ratios and 95% confidence intervals
exp(cbind(coef(coxph_model), confint(coxph_model)))

# Test the proportional hazards assumption
cox.zph(coxph_model)

# Plot the survival curves
library(survminer)
ggsurvplot(survfit(coxph_model), data=larynx)

```

```{r}
library(survival)

# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data for survival analysis
larynx$time[larynx$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(larynx$time))
drd <- larynx[, c("sex", "ph.ecog", "ph.karno", "wt.loss", "time", "status")]
drd$sex <- as.factor(drd$sex)
drd$ph.ecog <- as.numeric(scale(drd$ph.ecog))
drd$ph.karno <- as.numeric(scale(drd$ph.karno))
drd$wt.loss <- as.numeric(scale(drd$wt.loss))

# Fit Cox proportional hazards model
coxph.model <- coxph(Surv(time, status) ~ sex + ph.ecog + ph.karno + wt.loss, data = drd)

# Summarize Cox proportional hazards model
summary(coxph.model)

# Plot the survival curve
plot(survfit(coxph.model), main = "Survival Curve", xlab = "Days", ylab = "Survival Probability")
coxph.model <- coxph(Surv(time, status) ~  sex +  ph.ecog + ph.karno +  wt.loss  ,data= drd)
summary(coxph.model)
```
XXXXXXXXXXXXX
```{r}
# Load required packages
# Load required packages
library(survival)
library(tidyverse)
library(mice)

# Load data
data(cancer, package="survival")
larynx <- lung

# Convert variables to required format
larynx$age <- as.numeric(scale(larynx$age))
larynx$inst <- as.factor(larynx$inst)
larynx$sex <- as.factor(scale(larynx$sex))
larynx$ph_ecog <- as.numeric(scale(larynx$ph.ecog))
larynx$ph_karno <- as.numeric(scale(larynx$ph.karno))
larynx$pat_karno <- as.numeric(scale(larynx$pat.karno))
larynx$meal_cal <- as.numeric(larynx$meal.cal)
larynx$wt_loss <- as.numeric(larynx$wt.loss)
larynx$status <- as.factor(larynx$status)
larynx$time[larynx$status == 1] <- NA # Censored

# Impute missing data for institution 33
larynx$inst[larynx$inst == 33] <- NA
mice_imputed <- mice(larynx, m = 5, maxit = 50, method = 'pmm', seed = 500)
larynx_imputed <- complete(mice_imputed, 1)

# Fit Cox proportional hazards model
coxph.model <- coxph(Surv(time, status) ~ inst + sex + age + ph_ecog + ph_karno + pat_karno + wt_loss + meal_cal, data = larynx_imputed)
summary(coxph.model)

```

```{r}
library(survival)
library(rms)

# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data for survival analysis
larynx$time[larynx$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(larynx$time))
drd <- larynx[, c("sex", "ph.ecog", "ph.karno", "wt.loss", "time", "status")]
drd$sex <- as.factor(drd$sex)
drd$ph.ecog <- as.numeric(scale(drd$ph.ecog))
drd$ph.karno <- as.numeric(scale(drd$ph.karno))
drd$wt.loss <- as.numeric(scale(drd$wt.loss))


# Fit a flexible parametric survival model
fph.model <- psm(Surv(time, status) ~ rcs(ph.ecog, 4) + rcs(ph.karno, 4) + rcs(wt.loss, 4) + sex, data = drd, n.knots = 4)

# Summarize the flexible parametric survival model
summary(fph.model)

# Plot the survival curve
plot(Predict(fph.model, fun = survplot), main = "Survival Curve", xlab = "Days", ylab = "Survival Probability")

```
```{r}
library(survival)
library(tidyverse)
library(mice)

# Load data
data(lung, package="survival")
larynx <- lung

# Extract variables of interest
vars <- c("age", "sex", "ph.ecog", "ph.karno", "pat.karno", "meal.cal", "wt.loss", "status")

# Create function to compute summary statistics
sum_stats <- function(x) {
  n_missing <- sum(is.na(x))
  n_non_missing <- sum(!is.na(x))
  mean <- mean(x, na.rm = TRUE)
  sd <- sd(x, na.rm = TRUE)
  median <- median(x, na.rm = TRUE)
  q1 <- quantile(x, 0.25, na.rm = TRUE)
  q3 <- quantile(x, 0.75, na.rm = TRUE)
  iqr <- q3 - q1
  max <- max(x, na.rm = TRUE)
  min <- min(x, na.rm = TRUE)
  
  res <- c(n_missing = n_missing, n_non_missing = n_non_missing, mean = mean, 
           sd = sd, median = median, q1 = q1, q3 = q3, iqr = iqr, max = max, min = min)
  return(res)
}

# Compute summary statistics for each variable
summary_stats <- larynx %>% 
  select(all_of(vars)) %>% 
  summarise_all(sum_stats) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(statistic = V1, age = V2, sex = V3, ph.ecog = V4, ph.karno = V5, pat.karno = V6, 
         meal.cal = V7, wt.loss = V8, status = V9)

# Add variable names to the table
var_names <- c("Age (years)", "Sex (0=female, 1=male)", "ECOG performance status", 
               "Karnofsky performance score (physician)", "Karnofsky performance score (patient)",
               "Calories/day", "Weight loss (lbs)", "Status (0=censored, 1=event)")
table_one <- cbind(variable = var_names, summary_stats)

# Print table one
print(table_one)

```


full model
Here, I first added a column to the dataset indicating missing values for institution 33. Then, I used the mice function to perform multiple imputations for the missing data using predictive mean matching (PMM). Finally, I completed the imputation process and updated the inst column in the original dataset with the imputed values.

After the imputation, I fitted the Cox proportional hazards model as you provided in your code.
```{r}
# Load required packages
library(survival)
library(tidyverse)
library(mice)

# Load data
data(lung, package="survival")
larynx <- lung

# Add censoring indicator
larynx$time[larynx$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(larynx$time))
cens <- cbind(larynx$time, is.censored)

# Convert variables to required format
larynx$age <- as.numeric(scale(larynx$age))
larynx$inst <- as.factor(larynx$inst)
larynx$sex <- as.factor(scale(larynx$sex))
larynx$ph.ecog <- as.numeric(scale(larynx$ph.ecog))
larynx$ph.karno <- as.numeric(scale(larynx$ph.karno))
larynx$pat.karno <- as.numeric(scale(larynx$pat.karno))
larynx$meal.cal <- as.numeric(larynx$meal.cal)
larynx$wt.loss <- as.numeric(larynx$wt.loss)

# Impute missing data for inst 33
larynx$inst_missing <- ifelse(larynx$inst == 33, NA, as.numeric(larynx$inst))
mice_impute <- mice(larynx, m = 5, maxit = 50, method = "pmm", seed = 500)
larynx_imputed <- complete(mice_impute, 1)
larynx$inst <- as.factor(larynx_imputed$inst_missing)

# Fit Cox proportional hazards model
coxph.model <- coxph(Surv(time, status) ~ inst + sex + age + ph.ecog + ph.karno + pat.karno + wt.loss + meal.cal, data = larynx)
summary(coxph.model)
X <- model.matrix(~status+ inst+sex+ age+ph.ecog +ph.karno+pat.karno +wt.loss+meal.cal, data =larynx)

cat("model
    {
    for (i in 1:n) {
    is.censored[i]~dinterval(time[i],cens[i,1])
    time[i]~dweib(alpha,lambda[i])
    lambda[i]=exp(-mu[i]*alpha)
    mu[i]=inprod(beta[],X[i,])

    }

    ### Define the priors
   for(l in 1:Nbetas){beta[l]~dnorm(0,0.001)}
   alpha ~ dunif(0,10)
    }", file="aspirinRE2.txt")



Nbetas = ncol(X)
Nbetas
d.jags <- list(n = nrow(larynx), time = larynx$time, cens = cens, X = X, Nbetas = ncol(X))
#d.jags <- list(n = nrow(larynx), time = larynx$time, cens = cens, X = X, Nbetas = ncol(X), data = X)
i.jags <- function(){ list(beta = rnorm(ncol(X)), alpha = runif(1)) }
p.jags <- c("beta", "alpha")
library("rjags")
m1 <- jags.model(data=d.jags,  file = "aspirinRE2.txt", inits=i.jags, n.chains=3)
update(m1, 1000)
```

```{r}

```



```{r}
# Load required packages
library(survival)
library(tidyverse)

# Load data
data(cancer, package="survival")
larynx=lung
larynx$time[larynx$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(larynx$time))
cens <- cbind(larynx$time, is.censored)

# Convert variables to required format
larynx$age <- as.numeric(scale(larynx$age))
larynx$inst <- as.factor(scale(larynx$inst))
larynx$sex <- as.factor(scale(larynx$sex))
larynx$ph_ecog <- as.numeric(scale(larynx$ph.ecog))
larynx$ph_karno <- as.numeric(scale(larynx$ph.karno))
larynx$pat_karno <- as.numeric(scale(larynx$pat.karno))
larynx$meal_cal <- as.numeric(larynx$meal.cal)
larynx$wt_loss <- as.numeric(larynx$wt.loss)
X <- model.matrix(~status+ inst+sex+ age+ph.ecog +ph.karno+pat.karno +wt.loss+meal.cal, data =larynx)

# Define JAGS model
cat( "model {
  for (i in 1:n) {
    is.censored[i] ~ dinterval(time[i], cens[i,1])
    time[i] ~ dweib(alpha, lambda[i])
    lambda[i] <- exp(-mu[i] * alpha)
    mu[i] <- inprod(beta[], X[i,])
  }

  # Define the priors
  alpha ~ dunif(0,10)
  for (l in 1:Nbetas) {
    beta[l] ~ dnorm(0, 0.001)
  }
}",file="jags.code.txt" )

# Prepare data for JAGS
Nbetas <- ncol(X)
data.list <- list(n = nrow(larynx),
                  time = larynx$time,
                  is.censored = is.censored,
                  cens = cens,
                  X = X,
                  Nbetas = Nbetas)

# Set initial values for JAGS
initss <- function() {
  list(alpha = runif(1, 0, 10),
       beta = rnorm(Nbetas, 0, 0.1))
}

# Compile JAGS model
library(rjags)
jags.model <- jags.model(jags.code, data = data.list, inits = inits, n.chains = 3)

# Burn-in and run the model
update(jags.model, 1000)
samples <- coda.samples(data=data.list, file="jags.code.txt",inits=initss,variable.names = c("alpha", "beta"), n.iter = 5000)

# Summarize results
summary(samples)
plot(samples)

```



modified model
```{r}
library(rjags)
library(survival)

# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data for JAGS
drd <- larynx[, c("sex", "ph.ecog", "ph.karno", "wt.loss", "time", "status")]
drd$time[drd$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(drd$time))
cens <- cbind(drd$time, is.censored)
drd$sex <- as.factor(drd$sex)
drd$ph.ecog <- as.numeric(scale(drd$ph.ecog))
drd$ph.karno <- as.numeric(scale(drd$ph.karno))
drd$wt.loss <- as.numeric(scale(drd$wt.loss))

# Define JAGS model
jags.model <- "
model {
  # Priors
  beta0 ~ dnorm(0, 1.0E-6)
  for (j in 1:p) {
    beta[j] ~ dnorm(0, 1.0E-6)
  }
  sigma ~exp( dnorm(0, 1.0E-6))
  
  # Hazard function
  for (i in 1:n) {
    lambda[i] <- exp(beta0 + inprod(beta[], X[i,]))
    S[i, 1] <- 1
    for (t in 2:T) {
      S[i, t] <- S[i, t-1] * exp(-lambda[i] * d[t-1])
    }
    y[i] ~ dinterval(d[1], T, S[i, ])
  }
  
  # Likelihood for censored observations
  for (i in 1:n) {
    if (is.censored[i]) {
      S[i, T+1] <- S[i, T]
      cens[i, 2] ~ dbern(S[i, T+1])
    }
  }
}
"

# Set JAGS parameters
params <- c("beta0", "beta", "sigma", "lambda")

# Set initial values for JAGS
p <- ncol(X)
i.k <-function() {list(beta0 = 0, beta = rep(0, p), sigma=1)}

# Set up data for JAGS
data.jags <- list(n = nrow(X), T = ncol(cens), X = X, y = cens[, 1], is.censored = is.censored, cens = cens)

# Compile JAGS model
jags.model <- jags.model(textConnection(jags.model), data = data.jags, n.chains = 3,inits =i.k)
update(jags.model, 1000)

# Run MCMC simulations
samples <- coda.samples(jags.model, variable.names = params, n.iter = 5000)

# Summarize posterior distribution
summary(samples)

```
modified model 3
```{r}
library(survival)
data(cancer, package="survival")

data(cancer, package="survival")
larynx=lung


 # Survival and censoring times
aud=larynx
cens <- matrix(c(larynx$time, rep(NA, length(larynx$time))),nrow = length(larynx$time), ncol = 2)
larynx$time[larynx$status== 1] <- NA # Censored
is.censored <- as.numeric(is.na(larynx$time))
drd=larynx[,c(2,3,5,6,7,10)]
drd
#drd$inst <- as.factor((drd$inst))
drd$sex <- as.factor((drd$sex))
drd$ph.ecog <-as.numeric(scale(drd$ph.ecog))
drd$ph.karno <- as.numeric(scale(drd$ph.karno))
drd$wt.loss<- as.numeric(scale(drd$wt.loss))
X <- model.matrix(~status+ sex+ ph.ecog +ph.karno +wt.loss, data =drd)
cat("model
    {
    for (i in 1:n) {
    is.censored[i]~dinterval(time[i],cens[i,1])
    time[i]~dweib(alpha,lambda[i])
    lambda[i]=exp(-mu[i]*alpha)
    mu[i]=inprod(beta[],X[i,])

    }

    ### Define the priors
   for(l in 1:Nbetas){beta[l]~dnorm(0,0.001)}
   alpha ~ dunif(0,10)
    }", file="aspirinRE2.txt")



Nbetas = ncol(X)
Nbetas
d.jags <- list(n = nrow(drd), time = drd$time, cens = cens, X = X, Nbetas = ncol(X))
i.jags <- function(){ list(beta = rnorm(ncol(X)), alpha = runif(1)) }
p.jags <- c("beta", "alpha")
library("rjags")
m1 <- jags.model(data=d.jags,  file = "aspirinRE2.txt", inits=i.jags, n.chains=3)
update(m1, 1000)
```

trial4
```{r}
library(rjags)
library(survival)

# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data for JAGS
drd <- larynx[, c("sex", "ph.ecog", "ph.karno", "time", "status")]
drd$time[drd$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(drd$time))
cens <- cbind(drd$time, is.censored)
drd$sex <- as.factor(drd$sex)
drd$ph.ecog <- as.numeric(scale(drd$ph.ecog))
drd$ph.karno <- as.numeric(scale(drd$ph.karno))
X <- model.matrix(~ sex + ph.ecog + ph.karno, data = drd)

# Define JAGS model
jags.model <- "
model {
  # Priors
  beta0 ~ dnorm(0, 1.0E-6)
  for (j in 1:p) {
    beta[j] ~ dnorm(0, 1.0E-6)
  }
  log(sigma) ~ dnorm(0, 1.0E-6)
  
  # Hazard function
  for (i in 1:n) {
    lambda[i] <- exp(beta0 + inprod(beta[], X[i,]))
    S[i, 1] <- 1
    for (t in 2:T) {
      S[i, t] <- S[i, t-1] * exp(-lambda[i] * d[t-1])
    }
    y[i] ~ dinterval(d[1], T, S[i, ])
  }
  
  # Likelihood for censored observations
  for (i in 1:n) {
    if (is.censored[i]) {
      S[i, T+1] <- S[i, T]
      cens[i, 2] ~ dbern(S[i, T+1])
    }
  }
}
"

# Set JAGS parameters
params <- c("beta0", "beta", "sigma", "lambda")

# Set initial values for JAGS
p <- ncol(X)
inits <- list(beta0 = 0, beta = rep(0, p), log(sigma) = 0)

# Set up data for JAGS
data.jags <- list(n = nrow(X), T = ncol(cens), X = X, y = cens[, 1], is.censored = is.censored, cens = cens)

# Compile JAGS model
jags.model <- jags.model(textConnection(jags.model), data = data.jags, n.chains = 3)
update(jags.model, 1000)

# Run MCMC simulations
samples <- coda.samples(jags.model, variable.names = params, n.iter = 5000)

# Summarize posterior distribution
summary(samples)

```


```{r}


# Load required packages
library(survival)
library(tidyverse)

# Load data
data(cancer, package="survival")
larynx=lung
larynx$time[larynx$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(larynx$time))
cens <- cbind(larynx$time, is.censored)
# Convert variables to required format
larynx$age <- as.numeric(scale(larynx$age))
larynx$inst <- as.factor(scale(larynx$inst))
larynx$sex <- as.factor(scale(larynx$sex))
larynx$ph_ecog <- as.numeric(scale(larynx$ph.ecog))
larynx$ph_karno <- as.numeric(scale(larynx$ph.karno))
larynx$pat_karno <- as.numeric(scale(larynx$pat.karno))
larynx$meal_cal <- as.numeric(larynx$meal.cal)
larynx$wt_loss <- as.numeric(larynx$wt.loss)
X <- model.matrix(~status+ sex+ age+ph.ecog +ph.karno+pat_karno +wt.loss+meal_cal, data =larynx)

# Define the JAGS model
cat("model {
  # Prior distributions
  beta[1:Nbetas] ~ dmnorm(mu_beta[], Sigma_beta[,])
  alpha ~ dunif(0,10)
  sigma ~ dunif(0, 100)

  # Likelihood
  for (i in 1:n) {
    is.censored[i] ~ dinterval(time[i], cens[i,1])
    time[i] ~ dweib(alpha, exp(-mu[i]*alpha))
    mu[i] <- inprod(beta[], X[i,])
  }
  
  # Priors for hyperparameters
  mu_beta[1:Nbetas] ~ dnorm(0, 1.0E-6)
  Sigma_beta[1:Nbetas, 1:Nbetas] ~ dwish(R, nu)
}", file="model.txt")

# Data and initial values
list_data=list(
  n = nrow(larynx),
  Nbetas = ncol(X),
  time = larynx$time,
  is.censored = is.censored,
  cens = cens,
  X = X
)
i.jags <- function(){ list(
  R = diag(Nbetas),
  nu = Nbetas + 2,
  mu_beta = rep(0, Nbetas),
  Sigma_beta = diag(Nbetas),
  sigma = 1,
  alpha = 1)}
# Compile the JAGS model
library(rjags)
jags_model <- jags.model("model.txt", data = list_data,init=j.jags, n.chains = 3)

# Burn-in and update the model
update(jags_model, 1000)

# Run the MCMC chains and collect the samples
samples <- coda.samples(jags_model, variable.names = c("beta", "alpha", "sigma"), n.iter = 10000)


```





```{r}
library(rjags)
library(survival)

# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data for JAGS
aud <- larynx
drd <- larynx[, c(2, 3, 5, 6, 7, 10)]
drd$time[drd$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(drd$time))
cens <- cbind(drd$time, is.censored)
drd$sex <- as.factor(drd$sex)
drd$ph.ecog <- as.numeric(scale(drd$ph.ecog))
drd$ph.karno <- as.numeric(scale(drd$ph.karno))
drd$wt.loss <- as.numeric(scale(drd$wt.loss))
X <- model.matrix(~status + sex + ph.ecog + ph.karno + wt.loss, data=drd)

# Define JAGS model
p <- ncol(X)
jags.model <- "
model {
  # Priors
  beta0 ~ dnorm(0, 1.0E-6)
  for (j in 1:p) {
    beta[j] ~ dnorm(0, 1.0E-6)
  }
  log(sigma) ~ dnorm(0, 1.0E-6)
  
  # Hazard function
  for (i in 1:n) {
    lambda[i] <- exp(beta0 + inprod(beta[], X[i,]))
    S[i, 1] <- 1
    for (t in 2:T) {
      S[i, t] <- S[i, t-1] * exp(-lambda[i] * d[t-1])
    }
    y[i] ~ dinterval(d[1], T, S[i, ])
  }
  
  # Likelihood for censored observations
  for (i in 1:n) {
    if (is.censored[i]) {
      S[i, T+1] <- S[i, T]
      cens[i, 2] ~ dbern(S[i, T+1])
    }
  }
}
"

# Set JAGS parameters
params <- c("beta0", "beta", "sigma", "lambda")

# Set initial values for JAGS
inits <- list(beta0 = 0, beta = rep(0, p), log(sigma) = 0)

# Set up data for JAGS
data.jags <- list(n = nrow(X), T = ncol(cens), X = X, y = cens[, 1], is.censored = is.censored, cens = cens)

# Compile JAGS model
jags.model <- jags.model(textConnection(jags.model), data = data.jags, n.chains = 3)
update(jags.model, 1000)

# Run MCMC simulations
samples <- coda.samples(jags.model, variable.names = params, n.iter = 5000)

#

```
```{r}
library(rjags)
library(survival)

# Load data
data(cancer, package="survival")
larynx <- lung

# Prepare data for JAGS
aud <- larynx
drd <- larynx[, c(2, 3, 5, 6, 7, 10)]
drd$time[drd$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(drd$time))
cens <- cbind(drd$time, is.censored)
drd$sex <- as.factor(drd$sex)
drd$ph.ecog <- as.numeric(scale(drd$ph.ecog))
drd$ph.karno <- as.numeric(scale(drd$ph.karno))
drd$wt.loss <- as.numeric(scale(drd$wt.loss))
X <- model.matrix(~sex + ph.ecog + ph.karno + wt.loss, data = drd)

# Define JAGS model
jags.model <- "
model {
  # Priors
  beta0 ~ dnorm(0, 1.0E-6)
  for (j in 1:p) {
    beta[j] ~ dnorm(0, 1.0E-6)
  }
  log(sigma) ~ dnorm(0, 1.0E-6)
  
  # Hazard function
  for (i in 1:n) {
    lambda[i] <- exp(beta0 + inprod(beta[], X[i,]))
    S[i, 1] <- 1
    for (t in 2:T) {
      S[i, t] <- S[i, t-1] * exp(-lambda[i] * d[t-1])
    }
    y[i] ~ dinterval(d[1], T, S[i, ])
  }
  
  # Likelihood for censored observations
  for (i in 1:n) {
    if (is.censored[i]) {
      S[i, T+1] <- S[i, T]
      cens[i, 2] ~ dbern(S[i, T+1])
    }
  }
}
"

# Set JAGS parameters
params <- c("beta0", "beta", "sigma", "lambda")

# Set initial values for JAGS
p <- ncol(X)
inits <- function(){list(beta0 = 0, beta = rep(0, p), log(sigma) = 0)}

# Set up data for JAGS
data.jags <- list(n = nrow(X), T = ncol(cens), X = X, y = cens[, 1], is.censored = is.censored, cens = cens)

# Compile JAGS model
jags.model <- jags.model(textConnection(jags.model), data = data.jags, n.chains = 3)
update(jags.model, 1000)

# Run MCMC simulations
samples <- coda.samples(jags.model, variable.names = params, n.iter = 5000)

# Summarize posterior distribution
summary(samples)

```
```{r}
library(survival)
library(rjags)

# Load data
data(cancer, package = "survival")
lung <- lung[, c("time", "status", "sex", "ph.ecog", "ph.karno")]

# Prepare data for JAGS
lung$time[lung$status == 1] <- NA # Censored
is.censored <- as.numeric(is.na(lung$time))
cens <- cbind(lung$time, is.censored)
lung$sex <- as.numeric(lung$sex == "M")
lung$ph.ecog <- as.numeric(scale(lung$ph.ecog))
lung$ph.karno <- as.numeric(scale(lung$ph.karno))
X <- model.matrix(~ sex + ph.ecog + ph.karno, data = lung)

# Define JAGS model
jags.model <- "
model {
  # Priors
  beta0 ~ dnorm(0, 1.0E-6)
  for (j in 1:p) {
    beta[j] ~ dnorm(0, 1.0E-6)
  }
  log(sigma) ~ dnorm(0, 1.0E-6)

  # Hazard function
  for (i in 1:n) {
    lambda[i] <- exp(beta0 + inprod(beta[], X[i, ]))
    S[i, 1] <- 1
    for (t in 2:T) {
      S[i, t] <- S[i, t - 1] * exp(-lambda[i] * d[t - 1])
    }
    y[i] ~ dinterval(d[1], T, S[i, ])
  }

  # Likelihood for censored observations
  for (i in 1:n) {
    if (is.censored[i]) {
      S[i, T + 1] <- S[i, T]
      cens[i, 2] ~ dbern(S[i, T + 1])
    }
  }
}
"

# Set JAGS parameters
params <- c("beta0", "beta", "sigma", "lambda")

# Set initial values for JAGS
inits <- list(beta0 = 0, beta = rep(0, p), log(sigma) = 0)

# Set up data for JAGS
data.jags <- list(n = nrow(X), T = ncol(cens), X = X, y = cens[, 1], is.censored = is.censored, cens = cens)


```

